---
title: Computer Vision & Natural Language Processing Applications in the Insurance
  Industry
author: "Aaron Miles"
date: "11/02/2018"
output:
  slidy_presentation: default
  ioslides_presentation: default
  beamer_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(magick)
library(kableExtra)

cfpb <- read_csv('Consumer_Complaints.csv')


# Fixvariablenames
names(cfpb) <- tolower(gsub("[^[:alnum:]]","",names(cfpb)))


# Remove NonComplaints (results in ~320,000 cases)
cfpb <- cfpb %>%
  filter(!is.na(consumercomplaintnarrative), !is.na(product)) %>%
  group_by(product) %>%
  mutate(n_cases=n()) %>%
  filter(n_cases>10000)

table <- cfpb %>%
  select(consumercomplaintnarrative, product)


```

## About Me

**Education**

- Social Scientist turned Data Scientist
- Undergrad at BYU, Grad School at OSU

**Work**

- Past
    + Marketing Analyst/Data Scientist at Express
    + Data Scientist at The Shipyard
- Current
    + Data Scientist at Columbus Collaboratory


## Structured and Unstructured Data

- Structured Data: 

    + Relational Databases
    + Spreadsheets
    + Tables, etc.
  
- Unstructured Data: 

    + Images
    + Text
    + Video

## Structured and Unstructured Data

- Structured Data: 

    + Old Reliable
    + Still Lots of Value
  
- Unstructured Data: 

    + Wild West
    + Prime ground for innovation and value extraction

- Why?

    + Previously unanalyzed
    + Closer to what the user experiences
    + More nuanced


## Structured and Unstructured Data

**Burtch Works Classification**

- Work with unstructured data? Data Scientist
- Work only with structured data? Predictive Analytics Professional

## Why Unstructured Data Now?

Advances in:

- Storage
- Computing Efficiency
- Algorithmic Breakthroughs (Backpropogation)

## Types of Questions

Machine Learning typically answers three types of questions:

- Regression: How much?

- Classification: Which group?

- Clustering: How can this be split up?

- Detection: Where is it/are they?

## Examples

Where did I find examples?

- The Internet! People love to brag about what they're doing in this area
- Kaggle, A data science competition site
- Friends & Connections

## Computer Vision Example: Distracted Driving Detection

Using an image from a dashboard cam, can we classify what this person is doing into 10 classes:

    - Normal Driving
    - Texting (Left or Right)
    - Talking on the Phone (Left or Right)
    - Radio
    - Hair/Makeup
    - Talking to Passengers
    - Reaching Behind
    - Drinking

*Data from a competition sponsored by State Farm on Kaggle*

## Computer Vision Example: Distracted Driving Detection
```{r image_example, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}
file <- sample(list.files('imgs/test/'),4)

par(mfrow=c(2,2), mar=c(1,1,1,1))
paste('imgs/test/', file[1], sep='/') %>% image_read() %>% plot()
paste('imgs/test/', file[2], sep='/') %>% image_read() %>% plot()
paste('imgs/test/', file[3], sep='/') %>% image_read() %>% plot()
paste('imgs/test/', file[4], sep='/') %>% image_read() %>% plot()

```


## Other Computer Vision Examples

- Snapping images of accidents to assess damage
      + Could apply to homes as well
- Drones flying over disaster areas to assess the insurer's liability
- Estimate the CTR of a banner ad
- Webpage conversion optimization

## Natural Language Processing Example: Customer Complaint Classification

When a customer makes a complaint, how does it get to the right place? 

Identifying where it should go can be done automatically.

## Natural Language Processing Example: Customer Complaint Classification
```{r preview_table, echo=FALSE, message=FALSE, warning=FALSE}
knitr::kable(head(table), longtable=TRUE) %>%
  kable_styling(font_size = 15, bootstrap_options = c("striped", "hover")) %>%
  scroll_box(width = "725px", height = "450px")

```


## Other Natural Language Processing Examples

- Augmenting Chatbots
- Analyze how the brand is talked about on Social Media/News releases.
- Added input to fraud detection or claims management systems.

## Considerations

- Too big for laptops
- LOTS of tagged data needed
- Computing power (GPU's speed up processing, and are necessary for at least image analyses at meaningful scale)


## 

Questions?
